---
title: "Revealjs"
author: "Rafaela Becerra"
date: "February 2020"
output:
  revealjs::revealjs_presentation:
    theme: moon
    highlight: pygments
    center: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## {data-transition="zoom"}
<h1 style="background-color:#ff6347;">Dataset</h1>
<section data-background="image.jpg">
Data from cars.com in 2017 for a sample of 90 cars in Ohio of three models:
<span style="display: inline-block;" class="fragment fade-left" data-fragment-index="1">Mazda 6, </span>
<span style="display: inline-block;" class="fragment fade-left" data-fragment-index="2">Honda Accord, </span>
<span style="display: inline-block;" class="fragment fade-left" data-fragment-index="3">and Toyota Maxima.</span>
</section>

```{r, include = FALSE}
library(Stat2Data)
data("ThreeCars2017")
data=ThreeCars2017
```

## {data-background=#000000}
</br>
<h1 style="background-color:rgb(255, 99, 71);">The information given for each car is:</h1>

<section>
<p class="fragment fade-in-then-semi-out"">CarType: model</p>
<p class="fragment fade-in-then-semi-out">Age: years passed since production</p>
<p class="fragment fade-in-then-semi-out">Price: price ask by the owners, expressed in $1,000</p>
<p class="fragment fade-in-then-semi-out">Mileage: mileage in 1000</p>
</section>
## Lets look at "Mazda 6" observations:
```{r, echo=FALSE, include=FALSE, warning=FALSE}
library(plotly)
```

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.align="center"}
d <- data[data$CarType=="Mazda6",]

p <- plot_ly(
  d, x = ~Age, y = ~Mileage, text = ~paste("Mileage: ", Mileage, '$<br>Age:', Age),
  color = ~Price, size = ~Price
)

p

```

## Now, "Accord" observations:
```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.align="center"}
d <- data[data$CarType=="Accord",]

p <- plot_ly(
  d, x = ~Age, y = ~Mileage, text = ~paste("Mileage: ", Mileage, '$<br>Age:', Age),
  color = ~Price, size = ~Price
)

p

```

## Finnally, "Maxima" observations:
```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.align="center"}
d <- data[data$CarType=="Maxima",]

p <- plot_ly(
  d, x = ~Age, y = ~Mileage, text = ~paste("Mileage: ", Mileage, '$<br>Age:', Age),
  color = ~Price, size = ~Price
)

p

```


## The three joint: {data-background=#58D3F7}

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.align="center"}
p <- plot_ly(data, x = ~Age, y = ~Price, z = ~Mileage, color = ~CarType) %>%
   add_markers()%>%layout(scene = list(xaxis = list(title = 'Age from production'),
                     yaxis = list(title = 'Price in $1,000'),
                     zaxis = list(title = 'Mileage in 1,000')))
p

```

## {data-background=#000000}
<h1 style="border:2px solid DodgerBlue;">Some insights</h1>

<ul>
<li class="fragment roll-in" data-fragment-index="1">Accord, Mazda 6 and Massima can be comparable in terms of price.</li>
<li class="fragment roll-in" data-fragment-index="2">There are older Mazda 6 offer than Accord and Massima.</li>
<li class="fragment roll-in" data-fragment-index="3">Mileage has a higher impact on price than age. </li>
</ul>

<br/><br/>

<p class="fragment roll-in">For more information about the dataset and other datasets see: <https://www.rdocumentation.org/packages/Stat2Data/versions/2.0.0></p>
